Information Disclosure in Dynamic Innovation Contests

### 2025-05-26 paper/Paper.tex
update

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{Information Disclosure in Dynamic Innovation Contests}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{Information Disclosure in Dynamic Innovation Contests}

@@

@@

@@

\newpage

\section{Extension: Staggered Entry of Multiple Players}
\label{sect-extension}

@@

\newpage
\begin{APPENDICES}

>>>>

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{Bayesian Structural Inference for Dynamic Crowdsourcing Contests}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{Bayesian Structural Inference for Dynamic Crowdsourcing Contests}

@@

To Do: Contest Design Rules

\begin{proposition}
...
\end{proposition}

@@

\begin{figure}[!ht]
    \centering
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{validate_lamb.pdf}
        \caption{Validate $\lambda$}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{validate_sigma.pdf}
        \caption{Validate $\sigma$}
    \end{subfigure}
    \caption{Structure Validation}
    \label{fig-approximation}
\end{figure}

@@

@@

\begin{APPENDICES}

\section{Extensions}

\subsection{Staggered Entry of Multiple Players}
\label{sect-extension}

\subsection{Hybrid Kalman Filter}
\label{sect-kalman-filter}

% Submission
Let' suppose the submission events of the representative player $i$ occur at times $(t^i_1, t^i_2, ...)$ following an inhomogeneous Poisson process driven by the intensity function $\tau_i(t)$.

% Signal
After each submission, the contest designer emits a \textit{public} signal of the real output $x_{i,t_k}$. 
The signal is ambiguous and the game holder controls the ambiguity. 
The dynamic of signal is 
\begin{equation}\label{signal}
	\hat{x}_{i,k} = x_{i,t_k} + \frac{v_{i,k}}{\sqrt{\lambda}}, \quad k=1, 2, ...
\end{equation}
where $v_{i,k}$ follows standard normal distribution and is independent with $(W_{i,t})$ and $(W_{j,t})$, and the parameter $\lambda$ is set by the game holder to control the precision of signals. 
The larger the $\lambda$, the more accurate the signal would be.

% Bayesian Player
The information set of both players at time $t \ge 0$ is  $I_{t} := \{\hat{x}_{i,k}, \hat{x}_{j,k} : 0\le t_k \le t\}$. 
Both players estimate the unknown outputs $x_{i,t}$ and $x_{j,t}$ purely based on the information set $I_t$ and hidden actions $q_{i,t}$ and $q_{j,t}$. 
Let $\tilde{x}_{i,t} \equiv E(x_{i,t}|I_t)$ be the estimated output gap and $S_{i,t} \equiv E[(\tilde{x}_{i,t}-x_{i,t})^2|I_t]$ be the estimation variance. 
The conditional distribution $y_{t}|I_t\sim\mathcal{N}(\tilde{y}_{t},S_{t}|I_t)$ is fully captured by the mean $\tilde{y}_{t}$ and variance $S_{t}$.

The evolution of $\tilde{x}_{i,t}$ and $S_{i,t}$ is characterized by a continuous-discrete Kalman Filter (CD-KF, \citealt{barrau2017invariant}, \citealt{frogerais2012various}), with the measurement of each step $k=1, 2, ...$ consisting of two phases: in
(1) prediction phase during time interval $(t_{k-1}, t_{k})$, equations are derived from those of Kalman-Bucy filter \citep{Bensoussan1992Control} without considering the Kalman gain: 
\begin{align}
	d\tilde{x}_{i,t} &= q_{i,t}dt
	\label{filtered-x}\\
	dS_{i,t} &= \sigma^2dt
	\label{filtered-S}
\end{align} 
and in (2) updation phase $t=t_k$, equations are 
\begin{align}
	\tilde{x}_{i,k}^{+} &= \tilde{x}_{i,k}^{-} + \frac{\lambda S_{i,t_k}^{-}}{\lambda S_{i,t_k}^{-}+1}\left(\hat{x}_{i,k} - \tilde{x}_{i,t_k}^{-}\right)
	\label{updated-x}\\
	S_{i,t_k}^{+} &= \frac{S_{i,t_k}^{-}}{\lambda S_{i,t_k}^{-}+1} 
\end{align}
If $\lambda = 0$, we have $S_t = S_0+\sigma^2t$, i.e., the estimation variance is increasing in time linearly. 
If $\lambda > 0$, the estimation error decreases after each update of the public leaderboard, i.e., $S_{i,t_k}^+ < S_{i,t_k}^-$.
